---
title: "Assigment - kNN DIY"
author:
  - Willem Coster - Author
  - Ben van Vught - Reviewer
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
   html_notebook:
    toc: true
    toc_depth: 2
---


```{r}
library(tidyverse)
library(googlesheets4)
library(class)
library(caret)
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)    # alternatively, this also loads %>%
```

Choose a suitable dataset from [this](https://github.com/HAN-M3DM-Data-Mining/assignments/tree/master/datasets) folder and train  your own kNN model. Follow all the steps from the CRISP-DM model.


## Business Understanding

The "business" in the case is a research for HCV. The goal is to accurately guess when a blood donor has hepatitus.

## Data Understanding

According to the abstract given from the <a href="https://archive.ics.uci.edu/ml/datasets/HCV+data#"> Machine Learning Repository</a> the data set contains laboratory values of blood donors and Hepatitis C patients and demographic values like age.

```{r}
#Putting the given data sets in a variable
DF <- read.csv("https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/assignments/master/datasets/KNN-hcvdat0.csv")

# using str() to give some basic info
str(DF)
```

The dataset has 615 observations and 14 variables

## Data Preparation

Putting the given data sets in a variable
```{r}
# Cleaning the data (removing the first column, because it is a key)
cleanDF <- DF[-1]


#setting category to factor
cleanDF$Category <- factor(cleanDF$Category)
levels(cleanDF$Category) <- c("Donor", "Donor", "Hepatitis", "Hepatitis", "Hepatitis")

#setting Sex to creating a binary dimension for sex
cleanDF$Sex <- as.factor(cleanDF$Sex)
cleanDF <- cleanDF %>% 
    mutate(Sex = recode(Sex, 
                      "m" = "0", 
                      "f" = "1"))

cntDiag <- table(cleanDF$Category)
propDiag <- round(prop.table(cntDiag) * 100 , digits = 1)

cntDiag

propDiag
```



```{r}
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))
}

#replace empty values in rows for the mean of it's column
for(i in 4:ncol(cleanDF)){
  cleanDF[is.na(cleanDF[,i]), i] <- mean(cleanDF[,i], na.rm = TRUE)
}

#Creating normalized version of the cleaned data frame
cleanDF_n <- data.frame(Age = normalize(cleanDF$Age),Sex = cleanDF$Sex, ALB = normalize(cleanDF$ALB), ALP = normalize(cleanDF$ALP), ALT = normalize(cleanDF$ALT), AST = normalize(cleanDF$AST), BIL = normalize(cleanDF$BIL),  CHE = normalize(cleanDF$CHE), CHOL = normalize(cleanDF$CHOL), CREA = normalize(cleanDF$CREA), GGT = normalize(cleanDF$GGT), PROT = normalize(cleanDF$PROT))

summary(cleanDF_n)
```

Making training and test sets
```{r}
## 75% of the sample size
smp_size <- floor(0.75 * nrow(cleanDF_n))

## set the seed to make your partition reproducible
set.seed(22)
train_ind <- sample(seq_len(nrow(cleanDF_n)), size = smp_size)

trainDF_feat <- cleanDF_n[train_ind, ]
testDF_feat <- cleanDF_n[-train_ind, ]
trainDF_labels <- cleanDF[train_ind, 1]
testDF_labels <- cleanDF[-train_ind, 1]
```


## Modeling


```{r}
cleanDF_test_pred <- knn(train = as.matrix(trainDF_feat), test = as.matrix(testDF_feat), cl = as.matrix(trainDF_labels), k = 3)
cleanDF_test_pred
```


## Evaluation and Deployment


```{r}
confusionMatrix(cleanDF_test_pred, testDF_labels, positive = NULL, dnn = c("Prediction", "True"))
```

As seen above the accuracy of this KNN model equals 93,5%. It P-value scores lower than 0.05.

reviewer adds suggestions for improving the model